### 2019-04-01 Paper/Paper.tex
Work on paper through fleshing out future research

@@

@@

\begin{table}
  \hypertarget{Table 1}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c l c c}
    \hline
  Subjective Discount Factor & $\beta$ & $0.9949$ & Rotemberg Price Adjustment Cost & $\varphi$ & $100$ \\
   Frisch Labor Supply Elasticity & $1/\eta$ & $3$ & Inflation Gap Response & $\phi_\pi$ & $2.0$ \\
  Price Elasticity of Substitution & $\theta$ & $6$ & Output Growth Gap Response & $\phi_y$ & $0.5$ \\
  Steady-State Labor Hours & $\bar{n}$ & $1/3$ & Habit Persistence & $h$ & $0.80$ \\
  Steady-State Risk Premium & $\bar{s}$ & $1.0058$ & Risk Premium Persistence & $\rho_s$ & $0.80$ \\
  Steady-State Growth Rate & $\bar{g}$ & $1.0034$ & Notional Rate Persistence & $\rho_i$ & $0.80$ \\
  Steady-State Inflation Rate & $\bar{\pi}$ & $1.0053$ & Technology Growth Shock SD & $\sigma_g$ & $0.005$ \\
  Capital Share of Income & $\alpha$ & $0.35$ & Risk Premium Shock SD & $\sigma_s$ & $0.005$ \\
  Capital Depreciation Rate & $\delta$ & $0.025$ & Notional Interest Rate Shock SD & $\sigma_i$ & $0.0035$ \\
  Investment Adjustment Cost & $\nu$ & $4$ & & &\\
  \hline
  \end{tabular}
  \caption{Parameter values}
  \label{Tab:1}
\end{table}

@@

@@

  Richter et al. (2014) use Euler equation errors to measure the accuracy of their solutions. To measure errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method to allow exogenous variables to be off the grid. The Euler equation errors are reported in absolute value of the errors in base 10 logarithms. A consumption Euler equation error of -3 means the household makes an error equal to one out of every 1,000 consumption goods.

@@

\subsection{Solution Times}
\hyperlink{Table 2}{Table 2} reports the solution times for the Richter et al. (2013) and Gust et al. (2017) solution methods for the models with and without capital. The solution times were computed with multi-core processing using the Parallel Computing Toolbox. With MATLAB executable functions (MEX) provided by the companion Toolbox to Richter et al. (2013), we integrate Fortran in the interpolation steps of the algorithm. The solution times represent one run of each algorithm. The machine used to compute the solutions has two CPUs (at 2.30GHz), each with 16 cores. %Say something about the solution times%
\begin{itemize}
\item Gust et al. method slower, particularly on the model with capital. The differential blows up for the model with capital.
\item The speed and speed differential is influenced by the parameterization, and appears to take more time on the boundary of convergence for each algorithm.
\end{itemize}
\begin{table}[H]
  \centering
  \hypertarget{Table 2}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Iterations & Total Time & Iterations & Total time\\
    \hline
  Richter et al. (2013) & 67 & 17.9s & 65 & 0h 15m 37.1s\\    
  Gust et al. (2017) & 66 & 46s & 1170 &  5h 32m 48.6s\\
  \hline
\end{tabular}
  \caption{Solution times}
\end{table}

\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital. \hyperlink{Table 3}{Table 3} reports the RMSE and mean \% error from linear policy functions. The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.

@@

\begin{figure}[H]
\hypertarget{Figure 1}  
    \centering
    \includegraphics[scale=.6]{pfs3D_CAPITAL-eps-converted-to.pdf}%{pfs3D_CAPITAL.eps}
  \caption{Labor policy function for model with capital}    
  \label{Fig:1}
  \end{figure}

\begin{table}[H]
  \centering
  \hypertarget{Table 3}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Mean \% Error & RMSE & Mean \% Error & RMSE\\
    \hline
    Richter et al. policy & 0.46545\% &0.0020137 consumption units & 0.19585\% & .0029035 labor units \\    
  Gust et al. policy & 0.45556\% & 0.0019792 consumption units & 0.56142\% & 0.0076665 labor units \\
  \hline
\end{tabular}
  \caption{Smoothness measures for labor policy functions ($c$ for model with capital and $n$ for model with capital). Gust et al. combined policy functions are reported.}
\end{table}

@@

\begin{figure}[H]
\hypertarget{Figure 2}  
    \centering
    \includegraphics[scale=1.5]{eeerrors_C.eps}%{pfs3D_CAPITAL.eps}
  \caption{Euler equation errors for model with capital}    
  \end{figure}

\section{Conclusion}
% summarize results
Opportunities for future work
\begin{itemize}
\item Chebyshev polynomials
\item Smolyak grids
  \item This might make solution method faster, so we could potentially increase the number of grid points and make it better than Richter et al
  \end{itemize}

@@

\section{Results for model without capital} \hypertarget{Appendix C}
The following reports the corresponding results for the model wtihout capital. \hyperlink{Figure 3}{Figure 3} shows the cross-section of the consumption policy functions with the interest rate and risk premium. \hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the consumption euler Equation and the price Phillips curve.

\begin{figure}[H]
\hypertarget{Figure 3}  
    \centering
    \includegraphics[scale=.6]{pfs3D.eps}
  \caption{Consumption policy function for model without capital}    
  \end{figure}

@@

\begin{figure}[H]
\hypertarget{Figure 4}  
    \centering
    \includegraphics[scale=1.5]{eeerrors.eps}
  \caption{Euler equation errors for model without capital}    
  \end{figure}

>>>>

\section{Introduction}
As a result of the financial crisis of 2007-9 and the subsequent recession, central banks lowered their policy rate to its zero lower bound (ZLB). Although the ZLB constraint has always existed, for most of the data prior to the recession, policy rates were well above zero. In the wake of this unprecedented lowering of policy rates, the ZLB holds for a considerable portion of historic data for three major economies – the US, Japan, and Great Britain. The ZLB creates a kink in the policy rule and calls into question linear estimation methods. Researchers have responded to this inherent nonlinearity in different ways. Some have failed to incorporate the ZLB period data. Others have chosen to estimate linear models on the entire data set; however, this provides inaccurate estimates of model parameters and model predictions. A few have estimated nonlinear models that treats the ZLB as an occasionally binding constraint. As incorporating the ZLB constraint makes traditional solution methods intractable, researchers have turned to fully nonlinear models, including those described in Richter et al (2013) and Gust et al (2017). However, not much work has been done in comparing the accuracy and speed of different global nonlinear solution methods. We will examine the performance of Richter et al (2013) and Gust et al (2017) in terms of accuracy and speed.

@@

\begin{table}[H]
  \hypertarget{Table 1}
  \centering
    \captionsetup{justification=centering}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c l c c}
    \hline
  Subjective Discount Factor & $\beta$ & $0.9949$ & Rotemberg Price Adjustment Cost & $\varphi$ & $100$ \\
   Frisch Labor Supply Elasticity & $1/\eta$ & $3$ & Inflation Gap Response & $\phi_\pi$ & $2.0$ \\
  Price Elasticity of Substitution & $\theta$ & $6$ & Output Growth Gap Response & $\phi_y$ & $0.5$ \\
  Steady-State Labor Hours & $\bar{n}$ & $1/3$ & Habit Persistence & $h$ & $0.80$ \\
  Steady-State Risk Premium & $\bar{s}$ & $1.0058$ & Risk Premium Persistence & $\rho_s$ & $0.80$ \\
  Steady-State Growth Rate & $\bar{g}$ & $1.0034$ & Notional Rate Persistence & $\rho_i$ & $0.80$ \\
  Steady-State Inflation Rate & $\bar{\pi}$ & $1.0053$ & Technology Growth Shock SD & $\sigma_g$ & $0.005$ \\
  Capital Share of Income & $\alpha$ & $0.35$ & Risk Premium Shock SD & $\sigma_s$ & $0.005$ \\
  Capital Depreciation Rate & $\delta$ & $0.025$ & Notional Interest Rate Shock SD & $\sigma_i$ & $0.0035$ \\
  Investment Adjustment Cost & $\nu$ & $4$ & & &\\
  \hline
  \end{tabular}
  \caption{Parameter values}
  \label{Tab:1}
\end{table}

@@

@@

Another contribution of Gust et al (2017) is to solve their model using Smolyak discretization methods with Chebyshev polynomials. The Smolyak method, proposed by Smolyak (1963) and improved by Judd et al. (2014) is a sparse-grid method and thus avoids the curse of dimensionality associated with grid-based methods. However, we do not explore this difference in this paper.

@@

  We simulate 10,000 periods of the model at the nonlinear solution with random shocks. For each period, we follow one iteration of step 2 of the algorithm outlined in \hyperlink{Appendix B}{Appendix B} and then transform the residuals to Euler equation errors.

We considered adding a second measure of accuracy, a statistical measure from Den Haan and Marcet (1994) based on a transformation of the Euler equation residuals to a chi-square distribution. However, it proved uninformative, as several runs of the test statistic were all in the extreme tails of the distribution.

@@

\begin{table}[H]
  \centering
    \captionsetup{justification=centering}
  \hypertarget{Table 2}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Iterations & Total Time & Iterations & Total time\\
    \hline
  Richter et al. (2013) & 67 & 17.9s & 65 & 0h 15m 37.1s\\    
  Gust et al. (2017) & 66 & 46s & 1170 &  5h 32m 48.6s\\
  \hline
\end{tabular}
  \caption{Solution times}
\end{table}

\subsection{Solution Times}
\hyperlink{Table 2}{Table 2} reports the solution times for the Richter et al. (2013) and Gust et al. (2017) solution methods for the models with and without capital. The solution times were computed with multi-core processing using the Parallel Computing Toolbox. With MATLAB executable functions (MEX) provided by the companion Toolbox to Richter et al. (2013), we integrate Fortran in the interpolation steps of the algorithm. The solution times represent one run of each algorithm. The machine used to compute the solutions has two CPUs (at 2.30GHz), each with 16 cores. %Say something about the solution times%
\begin{itemize}
\item Gust et al. method slower, particularly on the model with capital. The differential blows up for the model with capital.
\item The speed and speed differential is influenced by the parameterization, and appears to take more time on the boundary of convergence for each algorithm.
\end{itemize}

\begin{figure}[H]
  \hypertarget{Figure 1}
  \centering
    \captionsetup{justification=centering}
    \includegraphics[scale=1.05]{pfs3DCAP.eps}
  \caption{Labor policy function for model with capital}    
  \end{figure}

\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital. The black dots on the nodes of the graph represent labor values corresponding to the ZLB.

\begin{table}[H]
  \centering
  \captionsetup{justification=centering}
  \hypertarget{Table 3}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Mean \% Error & RMSE & Mean \% Error & RMSE\\
    \hline
    Richter et al. policy & 0.46545\% &0.0020137 consumption units & 0.19585\% & .0029035 labor units \\    
  Gust et al. policy & 0.45556\% & 0.0019792 consumption units & 0.56142\% & 0.0076665 labor units \\
  \hline
\end{tabular}
  \caption{Smoothness measures for labor policy functions ($c$ for model with capital and $n$ for model with capital). Gust et al. combined policy functions are reported.}
\end{table}

\hyperlink{Table 3}{Table 3} reports the RMSE (root mean square error) and mean percent error from linear policy functions. The mean percent error is calculated as $1/N\sum_i^N |\textbf{pf.n}(i) - \hat{\textbf{n}}(i)|/\bar{n}$ where $N$ is the number of periods, $\textbf{pf.n}$ is the labor policy function, $\hat{\textbf{n}}$ is the linear regression model of $\textbf{pf.n}$ fit to the state variables, and $\bar{n}$ is steady state labor. The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.

@@

\begin{figure}[H]
\hypertarget{Figure 2}  
\centering
  \captionsetup{justification=centering}
    \includegraphics[scale=1]{eeerrorsCAP.eps}%{pfs3_CAPITAL.eps}
  \caption{Euler equation errors for model with capital}    
  \end{figure}

@@

\section{Conclusion}
% summarize results
Future work includes solving the Gust et al (2017) solution method using Smolyak discretization methods with Chebyshev polynomials. This would likely speed up the solution algorithm. We could increase the number of grid points to improve the accuracy of the solution with the regained time and compare this to the Richter et al (2013) solution method.

@@

\section{Results for model without capital} \hypertarget{Appendix C}
The following reports the corresponding results for the model without capital.

\begin{figure}[H]
\hypertarget{Figure 3}  
\centering
  \captionsetup{justification=centering}
    \includegraphics[scale=1]{pfs3D.eps}
  \caption{Consumption policy function for model without capital}    
  \end{figure}

\hyperlink{Figure 3}{Figure 3} shows the cross-section of the consumption policy functions with the interest rate and risk premium.

\begin{figure}[H]
  \hypertarget{Figure 4}
  \centering
    \captionsetup{justification=centering}
    \includegraphics[scale=.75]{eeerrors.eps}
  \caption{Euler equation errors for model without capital}    
  \end{figure}

\hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the consumption euler Equation and the price Phillips curve.

@@
